SUPPLEMENTARY INFORMATION: NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-04-19 SI.tex
Updates from Overleaf

\author[1]{Anne M. Kiirikki}         %ORCID: ?
\author[2]{Hanne S. Antila}          %ORCID: 0000-0002-2474-5053
\author[3]{Lara S. Bort}             %ORCID: ?
\author[4]{Pavel Buslaev}         %ORCID: 0000-0003-2031-4691
\author[5]{Fernando Favela}
\author[6]{Tiago Mendes Ferreira}
\author[7,8]{Patrick F.J. Fuchs}
\author[9]{Rebeca Garcia-Fandino}
\author[10]{Ivan Gushchin}
%\author[2]{Matti Javanainen}      %ORCID: 0000-0003-4858-364X
\author[11,12]{Batuhan Kav}           %ORCID: 0000-0003-4990-373X
\author[22]{Norbert Ku{\v c}erka}
\author[13]{Patrik Kula}
\author[14]{Milla Kurki}
\author[10]{Alexander Kuzmin}
\author[15,16]{Jesper J. Madsen}  %ORCID: 0000-0003-1411-9080
\author[17,18]{Markus S. Miettinen}   %ORCID: 0000-0002-3999-4722
%\author[2]{...}                   %ORCID: ?
\author[1]{Ricky Nencini}
\author[19]{Thomas Piggot}
\author[20]{{\'A}ngel Pi{\~n}eiro}
\author[10]{Suman Samantray}
\author[9,20,21]{Fabi{\'a}n Suarez-Leston}
\author[1,*]{O. H. Samuli Ollila} %ORCID: 0000-0002- 8728-1006
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[height = 0.9\textheight]{Figures/totalrankingCOMPL.pdf}
    \caption{Top 50 simulations in the NMRlipids Databank ranked based on the C--H bond order parameter quality against experiments.}
    \label{fig:top50simulations}
\end{figure}

>>>>

\author[1]{Anne M. Kiirikki}         %ORCID: ?
\author[2]{Hanne S. Antila}          %ORCID: 0000-0002-2474-5053
\author[3]{Lara S. Bort}             %ORCID: ?
\author[4]{Pavel Buslaev}         %ORCID: 0000-0003-2031-4691
\author[5]{Fernando Favela-Rosales}
\author[6]{Tiago Mendes Ferreira}
\author[7,8]{Patrick F.J. Fuchs}
\author[9]{Rebeca Garcia-Fandino}
\author[10]{Ivan Gushchin}
%\author[2]{Matti Javanainen}      %ORCID: 0000-0003-4858-364X
\author[11,12]{Batuhan Kav}           %ORCID: 0000-0003-4990-373X
\author[22]{Norbert Ku{\v c}erka}
\author[13]{Patrik Kula}
\author[14]{Milla Kurki}
\author[10]{Alexander Kuzmin}
\author[15,16]{Jesper J. Madsen}  %ORCID: 0000-0003-1411-9080
\author[17,18]{Markus S. Miettinen}   %ORCID: 0000-0002-3999-4722
%\author[2]{...}                   %ORCID: ?
\author[1]{Ricky Nencini}
\author[19]{Thomas Piggot}
\author[20]{{\'A}ngel Pi{\~n}eiro}
\author[10]{Suman Samantray}
\author[9,20,21]{Fabi{\'a}n Suarez-Leston}
\author[1,*]{O. H. Samuli Ollila} %ORCID: 0000-0002- 8728-1006
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[height = 0.85\textheight]{Figures/totalrankingCOMPL.pdf}
    \caption{Top 50 simulations in the NMRlipids Databank ranked based on the C--H bond order parameter quality against experiments. The columns 2-4 show qualities for acyl chain order parameters ($P^\mathrm{tails}$), headgroup order parameters ($P^\mathrm{hg}$), all order parameters ($P^\mathrm{total}$), and for X-ray scattering form factors ($FF_q$). Column 5 shows relative equilibration times for conformations ($\tau_\mathrm{rel}$). Note that the best possible order parameter quality is one, while the best possible form factor quality is zero. ID values in the last column can be used to identify each simulation in the databank.}
    \label{fig:top50simulations}
\end{figure}
